---
title: "Simulation Results for Linear Models (correlated errors)"
# author: "Haziq"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra)

model_codes <- readxl::read_excel("model_codes.xlsx") %>%
  mutate(code = paste0(x1, x2, x3, x1x2, x1x3, x2x3, x1x2x3, sep = ""))
beta_vals <- readxl::read_excel("model_codes.xlsx", sheet = "beta") %>%
  mutate(code = paste0(
    ifelse(x1 > 0, 1, 0),
    ifelse(x2 > 0, 1, 0),
    ifelse(x3 > 0, 1, 0),
    ifelse(x1x2 > 0, 1, 0),
    ifelse(x1x3 > 0, 1, 0),
    ifelse(x2x3 > 0, 1, 0),
    ifelse(x1x2x3 > 0, 1, 0),
    sep = "") %>% as.character()
  )


res_cleanup <- function(x) {
  # mutate(x, no = ifelse(prop < 0.05, NA, no)) %>%
  #   drop_na()
  x
  # x %>% 
  #   drop_na() %>%
  #   mutate(prop2 = prop,
  #          prop = prop / sum(prop))
}

res_final_tab <- function(x, true.mod = "1111111") {
  the.names <- names(x[c("iprior", "lasso", "spikeslab", "gprior")])
  do.call(bind_rows, mapply(cbind, x[c("iprior", "lasso", "spikeslab", "gprior")], 
                            "method" = the.names, SIMPLIFY = F)) %>%
    mutate(method = factor(method, levels = the.names)) %>%
    filter(mod == true.mod) %>%
    group_by(method) %>%
    select(mod, prop) 
}
```


# Summary

## Results for error sd = 3 and corr = 0.5


```{r, message = FALSE, echo = FALSE}
load("simres.RData")
res_tab <- NULL
for (i in seq_len(length(myres))) {
  res_tab <- bind_rows(res_tab,
                       res_final_tab(myres[[i]], beta_vals[i, 8, drop = TRUE]) 
  )
}
res_tab %>% 
  pivot_wider(names_from = method, values_from = prop) %>%
  replace(is.na(.), 0) %>%
  kbl(booktabs = TRUE, position = "h", digits = 2) %>%
  kable_styling(position = "center", latex_options = "HOLD_position")
```


\newpage

### Model `r beta_vals[1, 8, drop = TRUE]`

- True value: `r myres[[1]]$beta.true`
- `r paste0("nsim = ", myres[[1]]$nsim, ", n = ", myres[[1]]$n, ", corr = ", myres[[1]]$corr, ", err.sd = ", myres[[1]]$err.sd)`

```{r echo = FALSE}
lapply(myres[[1]][c("iprior", "lasso", "spikeslab", "gprior")], res_cleanup)
```
\newpage


### Model `r beta_vals[2, 8, drop = TRUE]`

- True value: `r myres[[2]]$beta.true`
- `r paste0("nsim = ", myres[[2]]$nsim, ", n = ", myres[[2]]$n, ", corr = ", myres[[2]]$corr, ", err.sd = ", myres[[2]]$err.sd)`

```{r echo = FALSE}
lapply(myres[[2]][c("iprior", "lasso", "spikeslab", "gprior")], res_cleanup)
```
\newpage


### Model `r beta_vals[3, 8, drop = TRUE]`

- True value: `r myres[[3]]$beta.true`
- `r paste0("nsim = ", myres[[3]]$nsim, ", n = ", myres[[3]]$n, ", corr = ", myres[[3]]$corr, ", err.sd = ", myres[[3]]$err.sd)`

```{r echo = FALSE}
lapply(myres[[3]][c("iprior", "lasso", "spikeslab", "gprior")], res_cleanup)
```
\newpage

### Model `r beta_vals[4, 8, drop = TRUE]`

- True value: `r myres[[4]]$beta.true`
- `r paste0("nsim = ", myres[[4]]$nsim, ", n = ", myres[[4]]$n, ", corr = ", myres[[4]]$corr, ", err.sd = ", myres[[4]]$err.sd)`

```{r echo = FALSE}
lapply(myres[[4]][c("iprior", "lasso", "spikeslab", "gprior")], res_cleanup)
```
\newpage

### Model `r beta_vals[5, 8, drop = TRUE]`

- True value: `r myres[[5]]$beta.true`
- `r paste0("nsim = ", myres[[5]]$nsim, ", n = ", myres[[5]]$n, ", corr = ", myres[[5]]$corr, ", err.sd = ", myres[[5]]$err.sd)`

```{r echo = FALSE}
lapply(myres[[5]][c("iprior", "lasso", "spikeslab", "gprior")], res_cleanup)
```
\newpage


### Model `r beta_vals[6, 8, drop = TRUE]`

- True value: `r myres[[6]]$beta.true`
- `r paste0("nsim = ", myres[[6]]$nsim, ", n = ", myres[[6]]$n, ", corr = ", myres[[6]]$corr, ", err.sd = ", myres[[6]]$err.sd)`

```{r echo = FALSE}
lapply(myres[[6]][c("iprior", "lasso", "spikeslab", "gprior")], res_cleanup)
```
\newpage


### Model `r beta_vals[7, 8, drop = TRUE]`

- True value: `r myres[[7]]$beta.true`
- `r paste0("nsim = ", myres[[7]]$nsim, ", n = ", myres[[7]]$n, ", corr = ", myres[[7]]$corr, ", err.sd = ", myres[[7]]$err.sd)`

```{r echo = FALSE}
lapply(myres[[7]][c("iprior", "lasso", "spikeslab", "gprior")], res_cleanup)
```
\newpage

### Model `r beta_vals[8, 8, drop = TRUE]`

- True value: `r myres[[8]]$beta.true`
- `r paste0("nsim = ", myres[[8]]$nsim, ", n = ", myres[[8]]$n, ", corr = ", myres[[8]]$corr, ", err.sd = ", myres[[8]]$err.sd)`

```{r echo = FALSE}
lapply(myres[[8]][c("iprior", "lasso", "spikeslab", "gprior")], res_cleanup)
```
\newpage




